Maximum Entropy Spectral Analysis

### 2021-02-17 paper/mesa.tex
changes in paper

% comments command
\newcommand{\an}[1]{{\textcolor{orange}{\texttt{AN: #1}} }}
\newcommand{\pr}[1]{{\textcolor{cyan}{\texttt{PR: #1}} }}
\newcommand{\fm}[1]{{\textcolor{blue}{\texttt{FM: #1}} }}
\newcommand{\sschmidt}[1]{{\textcolor{red}{\texttt{SS: #1}} }}
\newcommand{\BS}[1]{{\textcolor{green}{\texttt{SB: #1}} }}
\newcommand{\oldnewtxt}[2]{\sout{#1}\textcolor{red}{#2}}

@@

	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% ABSTRACT
\begin{abstract}
Burg method of Maximum Entropy Spectral Analysis (MESA) provides a powerful tool to perform spectral estimation of a time-series. The method is a generalization of Jaynes maximum entropy principle and provides the estimate for the spectrum in terms of the coefficients of some autoregressive order p process (AR(p)). The recursive solution requires a method for the estimate of the order $p$ for the process. Several methods are characterized on synthetic noise having a known power spectral density (PSD) via the computation of the percentage error and then compared.

@@

	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% TITLE
	\title{Maximum Entropy Spectral Analysis}
	\author{Alessandro \surname{Martini}}
		\email{martini.alessandr@gmail.com}
        \affiliation{Dipartimento di Fisica  Università di Pisa, and INFN Sezione di Pisa, Pisa I-56127,Italy}        
        %

@@

\section{Introduction}
\blindtext

\section{Theoretical foundations}
The Maximum Entropy principle (MAXENT) is one of the most important results in Bayesian Statistics. It provides a way to uniquely assign probabilities to a phenomenon in a way that best represent our state of knowledge, while at the same time it is non committal with unavailable information. Its domain of application turned out to be wider than expected. In fact, thanks to Burg \cite{burg1975maximum}, this method has also been applied to perform high quality computation of power spectral densities of time series. After a short introduction to Jayne's MAXENT, we will develop in detail Burg's technique of Maximum Entropy Spectral Analysis (MESA) and show that the estimate can be expressed in an analytical closed form.
for each outcome, i.e. appealing to the indifference principle (IP), is equivalent to the requirement for our experiment to be the most unpredictable. 
Consider now the opposite situation, in which probability is assigned appealing to IP and we have a different number of possible outcomes.
Intuitively, the most unpredictable experiment is the one with larger number of outcomes: probability of "getting it wrong" increases as $\frac{N -1}{N}$. So when equal probabilities are assigned, we want

\subsection{Maximum Entropy Spectral Analysis} 
The computation of the power spectral density is an important component in time series analysis and characterization. Also, if the process is at least wide sense stationary, PSD is related to the autocorrelation function via a Fourier Transform.

@@

The choice of a window function is arbitrary and made by trial and error, until a satisfactory compromise between variance and resolution of the estimate of power spectral density  is reached. A high frequency resolution implies high variance and vice-versa. Another problem is that the result is very unstable with respect to the window's choice, and this fact may raise the question of which we should consider as the "real" power spectral density. \\  
so that we can reformulate the variational problem requiring $S(f)$ to maximize the entropy gain. In real examples we have no access to all frequencies but only on those between minus and plus the Nyquist frequency, defined from the sampling interval $\Delta t$ as 
All our quantities are well defined in this range only, so that we are not going to maximize \ref{eq:EntropyGain}, but
Defining $\bar r_n$ as the sample autocorrelation, our constraints will be
This approach on power spectral density estimate was developed by Burg \cite{burg1975maximum} and it is a way out from the problems raised in periodograms estimate. It requires no assumptions on the unavailable estimates for $\bar r_n$ and is consistent with the sample autocorrelation function by construction. The hard task is now to show that this problem has a solution. Remarkably, it admits an analytical solution in a closed expression for $S(f)$ 
    S(f) = \frac{P_N \Delta t}{\left(\sum_{s=0}^N a_s z^z\right)\left(\sum_{s = 0}^N a^*_s z^{-s}\right)}, 
with $\Delta t$ the sampling interval $a_0$ = 1 and the coefficients $P_N$ and $a_i (i \neq 0)$ to be determined. The explicit solution can be found in Appendix REF

\subsection{Autoregressive Process Analogy} 
Consider an autoregressive stationary process of order $p$ (AR(p)): 
    x_t - b_1 x_{t-1} - b_2 x_{t-2} \dots b_p x_{t - p} = \nu_t, 

\subsection{Forecasting}

@@

	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% END & BIB

@@

\section{MESA solution}

@@

@@

@@

so that we can reformulate the variational problem requiring $S(f)$ to maximize the entropy gain. In real examples we have no access to all frequencies but only on those between minus and plus the Nyquist frequency, defined from the sampling interval $\Delta t$ as 

@@

All our quantities are well defined in this range only, so that we are not going to maximize \ref{eq:EntropyGain}, but

@@

Defining $\bar r_n$ as the sample autocorrelation, our constraints will be

@@

        \includegraphics[scale = 0.43]{Images/Noise and PSD/NormalPSDautocorr.pdf}

>>>>

% comments command
\newcommand{\wdp}[1]{{\textcolor{green}{\texttt{SS: #1}} }}
\newcommand{\amartini}[1]{{\textcolor{blue}{\texttt{SS: #1}} }}
\newcommand{\sschmidt}[1]{{\textcolor{red}{\texttt{SS: #1}} }}

@@

	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% ABSTRACT
\begin{abstract}
Burg method of Maximum Entropy Spectral Analysis (MESA) provides a powerful tool to perform spectral estimation of a time-series. The method is a generalization of Jaynes maximum entropy principle and provides the estimate for the spectrum in terms of the coefficients of some autoregressive process AR(p) or order $p$.
A closed form recursive solution provides an estimate of the autoregressive coefficients as well as of the order $p$ of the process.
We provide a ready to use implementation of the algorithm in the form of a python package `memspectrum`. We characterize our code performing a power spectral density analysis on some syntethic generated data (with known power spectral density) and we compare different criteria for stopping the recursion. Furthermore, we compare the performance of our code with the traditional Welch algorithm, using both syntethic data and real gravitational waves data from the LIGO-Virgo collaboration.
We find that, when compared to the Welch's method, the Burg's method provides a power spectral density (PSD) estimation with a systematically lower variance. This is particularly manifest in the case of a little number of datapoints, making Burg method most suitable to work in this regime.
%Several methods are characterized on synthetic noise having a known power spectral density (PSD) via the computation of the percentage error and then compared.

@@

	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% TITLE
	\title{Maximum Entropy Spectral Analysis}
	\author{Alessandro \surname{Martini}}
		\email{martini.alessandr@gmail.com}
        \affiliation{Dipartimento di Fisica  Università di Pisa, and INFN Sezione di Pisa, Pisa I-56127,Italy}        
	\author{Stefano \surname{Schmidt}}
		\email{s.schmidt@uu.nl}
        \affiliation{add me}      
	\author{Walter \surname{Del Pozzo}}
		\email{walter.delpozzo@unipi.it}
        \affiliation{Dipartimento di Fisica  Università di Pisa, and INFN Sezione di Pisa, Pisa I-56127,Italy}

@@

The study of the properties of a noisy process is a crucial task in many fields of physics and mathematical physics [Here we should make some examples...].
A particularly interesting class of stochastic processes are the so-called \textit{wide-sense} stationary processes. These are stochastic processes that display an invariance of their statistical properties, such as their two-point autocovariance function, with respect to time translation. If $x(t)$ is a wide-sense stationary process, it is completely determined by the knowledge of the auto-covariance function 
	R(\tau) = \mathbf{E}[x_t \cdot x_{t+\tau}]
or equivalently by the knowledge of their \emph{power spectral density} (PSD) $S(f)$. Thanks to the Wiener-Khinchin theorem the two are related by a Fourier transform: 
	S(f) = \int_{-\infty}^{\infty} \textrm{d}\tau R(\tau) e^{-i 2 \pi f \tau}\,.
In some literature, the PSD is introduced as  
\begin{equation}\label{eq:psd-f-definition}
	\mathbf{E}[\tilde{x}(f) \cdot \tilde{x}(f^\prime)] = S(f) \delta(f-f^\prime)
without highlighting its connection with the time structure of the process itself, thus masking some important properties that will explore further in what follows. The latter definition in (\ref{eq:psd-f-definition}) gives, however, i) a straightforward interpretation of the PSD: it measures how much signal ``power" is located in each frequency; ii) an operative way of estimating for an unknown process.  
%Under such assumption, it can be shown [cite something] that the problem of characterizing the noise properties is greatly simplified and its properties are summarized by a single \textit{autocorrelation function}, which describes how an observation at a given time correlates with another observation a later time. More formally, the properties of a zero mean time series $x_t$ are described by the function:
%\begin{equation}
%	R(\tau) = \mathbf{E}[x_t \cdot x_{t+\tau}]
%\end{equation}
%where the average is computed on different times $t$.
%Thus, a stationary noise time series is completely characterized by the autocorellation function.
%\par
%More often, the study is performed in frequency domain: indeed, for stationary noise the components in frequency $\tilde{x}(f)$ of a stationary time series are conditionally independent from each other. It can be shown that:
%\begin{equation}
%	\mathbf{E}[\tilde{x}(f) \cdot \tilde{x}(f^\prime)] = S(f) \delta(f-f^\prime)
%\end{equation}
%This equation defines the function \textit{power spectral density} (PSD) $S(f)$.
%The PSD has a straightforward interpretation: it measures how much signal ``power" is located in each frequency bin. Furthermore, it is not difficult to show that it is the Fourier transform of the autocorrelation function:
%\begin{equation}
%	S(f) = \int_{-\infty}^{\infty} \textrm{d}\tau R(\tau) e^{-i 2 \pi f \tau}
%\end{equation}
%A power spectral density fully describes a stationary noisy time series and this shows how important is in the study of noise.
%\par
%Thus, in many real application, the knowledge of the PSD is crucial for the understanding of the process and indeed algorithms for PSD computation are a standard part of every software package for computational physics.
An ubiquitous method for such computation is due to Welch \cite{Welch} and it based on the method of periodograms. Basically, the PSD is obtained by slicing the observed realisation $x(t_1),\ldots,x(t_n)$ of the process $x(t)$ into many windowed batches and averaging the squared moduli of their Fourier transforms. The standard approach of periodograms \cite{Lomb,Scargle} consists in taking the Fourier Transform of the sample autocorrelation, written as \begin{equation}

@@

The sequence $W$ is a window function that can be chosen in several different way, each choice presenting advantages and disadvantages for the final estimate of the PSD. \\ 
The choice of a window function is arbitrary and typically is made by trial and error, until a satisfactory compromise between variance and resolution of the estimate of PSD is reached. A high frequency resolution implies high variance and vice-versa. Moreover, the final result depends on the choice of window function, hence begging the question of what the ``real" PSD is. \\  
Another problem with this approach is the requirement for the window to be $0$ outside the interval: we are arbitrarily assuming $\rho_j = 0$ for $j > M$, and modifying the estimate if a non-rectangular window is chosen. Making assumptions on unobserved data and modifying the ones we have at our disposal introduces information about the process that is not really there. Moreover, this method requires a number of arbitrary choices to be made, e.g. the number of time slices, the kind of Window function, the overlap between consecutive slices, etc... All the knobs must be tuned by hand and their choice can dramatically affect the PSD estimation.
\par
An appealing alternative approach, based on the Maximum Entropy principle \cite{Jaynes}, has been put forward by Burg \cite{burg1975maximum}. Being rooted on solid theoretical foundations, we will see that Burg's method, unlike Welch's, does not require any preprocessing of the data and requires very little tuning of the arbitrary parameters, as it provides an iterative closed form expression for the spectrum of a stochastic time series. Furthermore, it embeds the PSD estimation problem into an elegant theoretical framework and makes minimal assumptions on the nature of the data.
Lastly and most importantly, it provides a robust link between spectral density estimation and the field of autoregressive processes. This provide a natural and simple machinery to forecast a time series, thus predicting past observations based on previous ones.
In this paper we discuss the details of the Maximum entropy principle, its application to Power Spectral Density estimation with Burg algorithm and the link between Burg's algorithm and autoregressive process. Furthermore, we present and describe a new code, `memspectrum`, that provides a robust python implementation of the algorithm.
We provide a thorough assessment of the performance of our code and we validate our results performing a number of tests. We compare our results with those of spectral analysis carried out with the standard Welch method.
\par
Our paper is organized as follows: blablabla...

\section{Theoretical foundations}
The Maximum Entropy principle (MAXENT) is among the most important results in Bayesian Statistics. It provides a way to uniquely assign probabilities to a phenomenon in a way that best represent our state of knowledge, while at the same time it is non committal with unavailable information. Its domain of application turned out to be wider than expected. In fact, thanks to Burg \cite{burg1975maximum}, this method has also been applied to perform high quality computation of power spectral densities of time series.

After a short introduction to Jayne's MAXENT (sec.~\ref{sec:MAXENT}), we will develop in detail Burg's technique of Maximum Entropy Spectral Analysis (MESA) and show that the estimate can be expressed in an analytical closed form (sec.~\ref{sec:MESA}).
Next, we will discuss an interesting link between Burg's method and autoregressive processes (sec.~\ref{sec:autoregr}) and in sec.~\ref{sec:forecasting} we will use such link to introduce a method for forecasting a time series.

\subsection{Maximum Entropy Principle} \label{sec:MAXENT}
\sschmidt{This section is yet to prune}
To introduce MAXENT as a variational problem, we will workout some simple examples to understand how information's entropy and `uncertainty' are related\footnote{
The word `information' will not be used to indicate our knowledge on the system under study: this is what we will call `evidence'. Information will be intended as in communication theory: it specifies the quantity of details needed to provide a full description of the system under study.
}.

If we consider a perfectly sinusoidal signal, knowledge of amplitude, frequency and phase are sufficient to fully reproduce it: it has a low information entropy content.
Even less information is required if we are studying a system whose outcome is certain (has probability $p = 1$).
If the amount of information $I$ can be considered to zero, a communication is not even needed.  
Shannon \cite{Shannon} proposed the quantity
\begin{equation}\label{eq:information}
    I = \log_2 \frac{1}{p(x)}
\end{equation}
to represent the quantity of information brought by an outcome $x$ with probability $p(x)$. It has the nice property of being an additive quantity and it is monotonically decreasing as a function of $p \in [0, 1]$. The more uncertain the outcome, the higher the information it brings.
\par
What happens if we consider a larger set of different events? What is  the `most uncertain' outcome?  Since we are intending probability as a representation of the state of knowledge, one of the first requirement for our assignment is the agreement with common sense.
Consider an experiment based on the occurrence of one of two different outcomes $E_1, E_2$ with given probabilities $P_1$ and $P_2$. What are the values that make our outcome the most uncertain?
If $P_1$ and $P_2$ are largely different, like $P_1 = 0.999$ and $P_2 = 0.001$, we have enough evidence to believe that event $E_1$ will occur almost certainly, considering $E_2$ to be a very implausible outcome.
The most unpredictable experiment is the one in which 
\begin{equation}\nonumber
    P_1 = P_2 = \frac{1}{2}:
\end{equation}
this describes a situation of `maximum ignorance'; we have no evidence at all and we have no instruments to predict what the outcome of such an experiment will be.  \\ 
This can be generalized in the case of $N$ events. Assigning same probability
\begin{equation*}
    P_1 = \dots = P_N = \frac{1}{N}
\end{equation*}
for each outcome, i.e. appealing to the indifference principle (IP), is equivalent to the requirement for our experiment to be the most unpredictable. 
All we know is that one over $N$ events is going to happen. With this evidence, we cannot expect one outcome to occur over the others. 
To report the results of such an experiment, we need to communicate every single outcome: it 'carries' high information. 
This description also makes clearer the role played by evidence: it has to be used in probability assignment in order to make the result 'more certain' or 'less informative'. It is clear from the point of view of communication theory: the higher the evidence on a system, the lower the information I need to send to describe it.
\par
It is now clear that any assignment different from the 'most uncertain' is violating the hypothesis for it to being non committal to non-available evidence. We can only assign a more certain probability, i.e. less informative, if we have evidence for it. If we have none, the result has to be the most unpredictable, i.e. the most informative. 
Assigning probabilities requires maximization of uncertainty using evidence as constraint. This looks like a variational problem, where a numerical measure of uncertainty $H\left[p_1, \dots, p_N\right]$ has to maximized. $H$ has to be a 'generalization' of information defined in equation (\ref{eq:information}) to be something like the 'expected information' brought by an experiment with $N$ possible outcomes each with its own probability $p_i$.

Some properties for $H$ can be worked out easily. 
From previous discussion, given a fixed number $N$ of possible outcomes, we want $H$ to be maximized by the choice $p_1 = \dots = p_N$.
Consider now the opposite situation, in which probability is assigned appealing to IP and we have a different number of possible outcomes.
Intuitively, the most unpredictable experiment is the one with larger number of outcomes: probability of "getting it wrong" increases as $\frac{N -1}{N}$. So when equal probabilities are assigned, we want
\begin{equation}
    \nonumber
    H\left[\frac{1}{N}, \dots, \frac{1}{N}\right]
\end{equation}
to increase monotonically with N.

We also want our function to be continuous in its parameters: any small change in probability has to slightly affect uncertainty. \\
Last is composition property. Consider three events with probability $p_1, p_2, p_3$ such that $p_2 + p_3 = 1 - p_1 = q$. We require 
\begin{equation}
    H\left(p_1, p_2, p_3\right) = H(p_1, q) + qH\left(\frac{p_2}{q}, \frac{p_3}{q}\right),
\end{equation}
so that uncertainty is additive.

Shannon \cite{Shannon} showed that the only functional form satisfying our assumptions is given by:
\begin{equation}\label{eq:entropy}
    H[p_1, \dots, p_N] = - \sum_{i = 1}^N p_i\log{p_i},
\end{equation}
or, in the continuous case:
\begin{equation}
    H[p(x)] = - \int p(x)\ln p(x) dx,
\end{equation}
and $H$ is what we will call entropy.

This interpretation is straigthforward: if we compare it with Eq.~(\ref{eq:information}), we see that the entropy is defined as the 'average information'. The probability assignments made maximizing it with respect to $p$, is somehow requiring  the 'expected value' of uncertainty to be a maximum. Such an assignment is in agreement with our hypothesis of being `non committal' with unavailable evidence, since \ref{eq:entropy} is all we need to assign probabilities uniquely. Evidence can be added in form of constraints in the maximization.

%It is easy to verify that this expression for entropy verifies the aforementioned properties. 
%Assigning the same value for each probability $p_i$, it is straightforward to verify $H$ increases with N: 
%\begin{equation}
%    -\sum_{i = 1}^N \frac{1}{N}\log{\frac{1}{N}} = - \log\frac{1}{N} = \log N.
%\end{equation}

To show how the maximization of entropy, supplemented with additional evidence, can provide a unique probability assignment, we will work out three examples.
In each of them, we will add more evindence (i.e. constraints on the optimization problem) and we will obtain different results.

First of all, we want to show that, in case in which our only constraint is exhaustiveness
$\sum_{i = 1}^{N}p_i = 1 $,
MAXENT reduces to indifference principle as it should be. The variational problem is defined as
\begin{equation}\label{eq:entropyNormConst}
    \delta\left[H - \lambda\sum_{i = 1}^N (p_i - 1)\right] = 0 
\end{equation}
with
\begin{equation}
    \delta H\left[p_1, \dots, p_N\right] = \sum_{i = 1}^N\frac{\partial H}{\partial p_i}\delta p_i = - \sum_{i = 1}^N\left(\log p_i + 1\right),
\end{equation}
so that equation \ref{eq:entropyNormConst} reduce to
\begin{equation}\nonumber 
    \sum_{i = 1}^N\left[\log p_i + \lambda + 1 \right]\delta p_i = 0\,.
\end{equation}
The solution of the previous equation is easily worked out requiring every term to be zero: 
\begin{equation}\nonumber 
    p_i = e^{-\lambda - 1}.
\end{equation}
Applying the normalization condition, it is immediate to show that
\begin{equation}
    p_i = \frac{1}{N}.
\end{equation}
MAXENT reduces to the IP when only the normalization constraint is used.

In the second example, we will add the constraint that the distribution has a known mean value: $\int \d{x} x p(x) = \bar{x}$. For simplicity we will work in the continuous case.
The variational problem can be rewritten as: 
\begin{equation}
    \int \left[\log p(x) + 1 + \lambda + \mu x \right]\delta p(x) = 0
\end{equation}
with constraints: 
\begin{equation*}
    \int \d{x} \; p(x)  = 1 \text{  and  }
    \int \d{x} \; x p(x) = \bar x.
\end{equation*}
For simplicity, we consider $x$ to be a variable ranging in the interval $(-\infty,+\infty)$, but this can be easily computed for every other interval.

The general solution for $p(x)$ is:
\begin{equation}
    p(x) = e^{-1 - \lambda - \mu x} 
\end{equation}
where $\lambda$ and $\mu$ are two Lagrange multipliers
The normalization conditions implies 
\begin{equation}\nonumber 
   1 =  \int \d{x} \; p(x) = e^{-1-\lambda}\int e^{-\mu x} dx, 
\end{equation}
so that: 
\begin{equation}\nonumber 
    e^{-1 -\lambda} = \mu.
\end{equation}
The fixed average condition provides a value for $\mu$ in terms of $\bar{x}$:
\begin{equation}
	\mu = \frac{1}{\bar{x}}
\end{equation}
The solution is then an exponential distribution:
\begin{equation}
    p(x) = \frac{1}{\bar{x}} \exp\left(-\frac{x}{\bar{x}}\right). \nonumber 
\end{equation}

Lastly, and more interestingly, we also consider a constraint on the variance. For this reason, we set:
\begin{align*}
    \int \d{x} \; p(x)  = 1 \text{  and  }
	\int \d{x} \; x p(x) = \bar{x} \\
	\text{  and  }
	\int \d{x} \; (x-\bar{x})^2 p(x)  = \sigma^2
\end{align*}
Performing the same computation as above, we obtain a well known result:
\begin{equation}
	p(x) = \frac{1}{\sigma\sqrt{2\pi}} e^{-\frac{1}{2}\left(\frac{x-\bar{x}}{\sigma}\right)^2}
\end{equation}

%Take a vector  $\vec x(t)$ with components in $\mathbb{R}^N$
%\begin{equation*}
%    \vec x(t) = \left(x_1, \dots, x_N \right), \quad \text{ with } x_i = x(t_i),
%\end{equation*}
%We assume $\vec x$ to be time dependent and real valued because we will work with time dependent single channel signals. If we put constraints in both mean $\vec \mu(t)$ and covariance matrix $C_(t_i, t_j)$, MAXENT allow us to assign for $\vec x(t)$ a multivariate normal distribution \cite{gregory_2005}: 
%\begin{align}
%    p&\left(\vec x(t)\vert I\right) = \nonumber \\
%    &\frac{1}{\left(2 \pi \det C\right)^{k / 2}}\exp\left(-\frac{1}{2}\sum_{i,j}(x_i-\mu_i) (x_j-\mu_j)C^{-1}_{ij} \right). 
%\end{align}
Thus MAXENT provide a deeper insight into the Gaussian distribution.
It is not only the limit distribution provided by the central limit theorem for finite variance processes but it is also the distribution that maximizes the entropy. For this reason, appealing to MAXENT principle, it is the correct assignment if mean and covariance are the only quantities that fully define our process. In some sense, we can interpret the central limit theorem as the natural `statistical' evolution toward a configuration that maximizes entropy.

\subsection{Maximum Entropy Spectral Analysis} \label{sec:MESA}
The computation of the power spectral density is an important component in stationary time series analysis and characterization.
In principle, if the autocorrelation was known exactly (i.e. at every time $\tau$), the computation of the PSD would be just a single Fourier transform.
However, in every realistic setting, we are dealing with a finite number of samples $N$ and it is not possible such precise computation.
Moreover, the error $\sigma_k$ in the estimate of the autocorrelation after $k$ steps increases with $k$ as $\sigma \sim \frac{1}{\sqrt{N - k}}$, so that only a few values for the autocorrelation function can actually be computed reliably.
This bring us the core of our problem: how to give an estimate from partial (and noisy) knowledge of the autocorrelation function? The Maximum Entropy Principle can guide use in this task without any a priori assumptions on the unavailable data\footnote{Indeed this is the largest difference with the most common Welch method. The latter assumes that the unknown values of the autocorrelation are $0$. Clearly, this assumption is unjustified and MAXENT is a good way to drop this assumption.}.
\par
As in the previous examples, we need to set up a variational problem where the entropy eq.~\ref{eq:entropy} is maximized with some problem-specific constraints. 
In our case, they are i) the PSD estimate has to be non-negative; ii) its Fourier transform has to match the sample autocorrelation (wherever an estimate of this is available).
\par
Before doing so, there is a technical problem to solve: our definition of entropy (eq.~\ref{eq:entropy}) depends on a probability distribution, not on the power spectrum. We then need to to formulate the variational problem in terms of the power spectral density $S(f)$ alone.
A way out of this is considering our signal as the result of filtering a white noise process with a filter whose power response is exactly $S(f)$ \cite{AblesMESA}. One can show that the 'entropy gain' obtained filtering white noise is: 
\begin{equation}\label{eq:EntropyGain}
    \Delta H = \int_{-\infty}^{\infty}\log S(f) df , 
\end{equation}
so that we can reformulate the variational problem requiring $S(f)$ to maximize the entropy gain \sschmidt{Non ho capito questa parte...:(}. In real examples we have no access to all frequencies but only on those between minus and plus the Nyquist frequency, defined from the sampling interval $\Delta t$ as 
\begin{equation}
    Ny = \frac{1}{2 \Delta t}.
\end{equation}
All our quantities are well defined in this range only, so that we are not going to maximize \ref{eq:EntropyGain}, but
\begin{equation}\label{eq:EntropyGain2}
    \Delta H = \int_{- Ny}^{Ny}\log S(f) df.
\end{equation}

Now the the objective to maximize is well defined, we can write down the constraints of our problem.
Defining $\bar r_n$ as the sample autocorrelation, we require that the variational solution $S(f)$ for the PSD matches the empirical autocorrelation. This means:
\begin{equation}\label{eq:MaxConstraint}
\int_{-Ny}^{Ny} S(f) e^{\imath 2 \pi f n \Delta t} df = \bar r_{n}.
\end{equation}
This approach on power spectral density estimate was developed by Burg \cite{burg1975maximum} and it is a way out from the problems raised in periodograms estimate. It requires no assumptions on the unavailable estimates for $\bar r_n$ and is consistent with the sample autocorrelation function by construction. Remarkably, it admits an analytical solution in a closed expression for $S(f)$.

\begin{equation}\label{eq:MESApsd}
    S(f) = \frac{P_N \Delta t}{\left(\sum_{s=0}^N a_s z^z\right)\left(\sum_{s = 0}^N a^*_s z^{-s}\right)}, 
\end{equation}
with $\Delta t$ the sampling interval $a_0$ = 1 and the coefficients $P_N$ and $a_i (i \neq 0)$ to be determined. The details of the derivation and the actual values of the coefficients $a_i$ can be found in appendix \ref{sec:MESA_solution}.

\subsection{Autoregressive Process Analogy} \label{sec:autoregr}
The application of MESA is not limited to spectral estimates, but it also provides a link between spectral analysis and the study
of autoregressive processes.\cite{doi:10.1029/RG013i001p00183}.
An autoregressive stationary process of order $p$ (AR(p)) is a time series whose values satisfy the following expression: 
\begin{equation} \label{eq:AR_p}
    x_t - b_1 x_{t-1} - b_2 x_{t-2} \dots b_p x_{t - p} = \nu_t
\end{equation}
where $b_1, \ldots, b_p$ are real coefficients and $\nu_t$ is white noise with a given variance $\sigma^2$.
Thus, an AR(p) process models the dependence on every point on the $p$ past observation, thus being potentially able to model complex autocorrelation between data.
\par
To show the analogy, we compute the PSD of such process and we show that it is formally equivalent to the PSD obtained in eq.~\ref{eq:MESApsd}.
We start taking the z \sschmidt{What is the z transform} transform of the previous eq.~\ref{eq:AR_p}: 
\begin{align}
    \sum_t x_t z^t - \sum_i b_i z^i\sum_t x_{t - i} z^{t - i} = \sum_t \nu_t z^t.
\end{align}
Calling $\tilde x(z)$ and $\tilde \nu (z)$, the transformed quantities, 
in the $z$ domain, the process takes the form:
\begin{equation}
    \tilde x(z) = \frac{\tilde\nu(z)}{\left(1 - \sum_{i = n}^p b_n z^n \right)}
\end{equation}
Since we assumed a stationary process, $\tilde{x}(z)$ is analytic both on and inside the unit circle. Taking its square value and evaluating it on the unit circle $z = e^{-\imath 2 \pi f \Delta t}$, from the definition of spectral density one obtains:
\begin{equation}\label{eq:ARspectrum}
    S(f) = \vert \tilde x(z)\vert ^ 2 = 
    \frac{\vert \tilde \nu(f) \vert ^ 2}{\left\vert 1 - \sum_{n = 1}^p b_i e^{\imath 2 \pi f n \Delta t} \right\vert ^ 2}.
\end{equation}
The numerator is the spectral density of white noise $\nu_t$, i.e. its (constant) variance $\sigma^2$.
Equation~\ref{eq:ARspectrum} and eq.~\ref{eq:MESApsd}) are equivalent, if we identify $b_i = - a_i$ and $P_N \Delta t= \sigma ^ 2$.
This shows that the MAXENT estimation of the PSD computes the coefficients of the autoregressive process that is able to model the data faithfully.

\sschmidt{I don't understand the next of this section...}
Having computed the prediction error filter one can easily obtain an estimate of the $AR$ coefficients for the process just changing sign to the prediction error filter $a_i$.
Taken a time series, MESA allows us to compute the power spectrum and to find an effective description in terms of an autoregressive process. 
Wold's theorem ensures that this (approximate) description for the phenomenon is legitimate when the process is found to be stationary. So, MESA defines a bridge between spectral estimation and the study of autoregressive processes, an unexpected and fundamental result. \\
Another very remarkable process for this estimate, is that the linear predictor obtained solving the error filter equation, is the best linear predictor, i.e. it minimizes error, and is equivalent to a least square fit for the coefficients. \cite{VDBos}  \\ 
To prove that it minimizes error, we will follow the original proof provided by Burg \cite{burg1975maximum}. Consider a general linear predictor $-c_i$: 
\begin{equation}
    x_{t} - \sum_{i = 1}^p (-c_i)x_{t - i} = \sum_{i = 0}^p c_i x_{t - i} = e'_t, 
\end{equation}
Denoting with $E\left[\cdot\right]$ the expectation value of some variable, the mean square error is given by: 
\begin{equation}
E\left[\sum_{i = 0}^p c_i x_{t-i}\sum_{j = 0}^p c^*_j x^*_{t - j}\right] = \sum_{i,j} c^*_j E\left[x^*_{t-j}x_{t-i} \right] c_j = \sum_{i, j}c^*_j R(j - i) c_i > 0,
\end{equation}
which, being $R$ positive definite and defined by the multiplication of a complex number times its complex conjugate, is always positive definite. 
Let $-\vec{b}$ be the prediction error filter obtained with MESA. Multiplying the left hand side of \ref{eq:predictionErrorFilter} for the complex conjugate of the forward prediction error, 
\begin{equation}\nonumber 
    \sum_{i,j}b^*_jR(j-i)b_i = P_N
\end{equation}
is obtained . \\ 
The (positive) quantity  
\begin{equation}\label{eq:linearPredictor}
    \sum_{j = 0}^p\sum_{i = 0}^p(c^*_j - b^*_j)R(j-i)(c_i - b_i),
\end{equation}
using Einstein notation on repeated indices and recall that $c_0 = b_0 = 1$, can be rewritten as 
\begin{align}
    & c^*_j R(j - i) c_i - c^*_j R(j - i) b_i - b^*_j R(j - i) c_i + b^*_j R(j - i)  b_i =\\ \nonumber 
    &c^*_j R(j - i) c_i - c^*_0 P_N - P_N c_0 + P_N =\\ \nonumber
    & c^*_j R(j - i) c_i - P_N.
\end{align}
Moving $P_N$ on the left hand side, it becomes 
\begin{equation}\label{eq:bestLinearPredictor}
    \sum_{i, j}c^*_j R(j-i)c_i = \sum_{j = 0}^p\sum_{i = 0}^p(c^*_j - b^*_j)R(j-i)(c_i - b_i) + P_N.
\end{equation}
Being all the quantities positive definite, the left hand side is minimized by the choice $c_i = b_i$. Also, known $P_N$, the previous equation gives an estimate on the additional mean square error associated at choices that differ from the prediction error filter.

\subsection{Forecasting} \label{sec:forecasting}
The link between MESA and autoregressive process allow us to forecast from a given time series, thus providing plausible future observation for the data.
Indeed, an autoregressive process of order $p$ models the conditional probability $p(x_t|x_{t-1}, \ldots , x_{t-p})$ of the observation at time $t$ with respect to the past $p$ observation:
\begin{align}\label{eq:p_forecast}
	p&(x_t|x_{t-1}, \ldots , x_{t-p}) \nonumber\\
	&= \frac{1}{\sigma\sqrt{2\pi}} \exp\left[-\frac{1}{2} \left(\frac{x_t - \sum_{i = 1}^p b_i x_{t-i}}{\sigma}\right)^2\right].
\end{align}
The interpretation of eq.~\ref{eq:p_forecast} is straightforward: $x_t$ follows a Guassian distribution with a fixed variance an a mean value $m_t = \sum_{i = 1}^p b_i x_{t-i}$ computed from past observations.
Equation~\ref{eq:p_forecast} provides then a well defined probability framework for predicting future observations: this is a very useful feature of the method, which does not have an equivalent in any other spectral analysis computation.

@@

	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% END & BIB
>>>>>>> dc2ea6b02d554f80ea49ef0c67cf14dcffc60bb8

@@

\section{MESA solution} \label{sec:MESA_solution}

@@

\begin{equation}\label{eq:MESApsd_appendix}

@@

   \frac{P_N}{2 \pi \imath} \oint _{\mathbb S^1}\frac{z^{-s - 1}}{\sum_{n = 0}^N a_n z^n \sum_{n = 0}^N a^*_n z^{-n}}dz = \bar r_s. 

@@

so that we can reformulate the variational problem requiring $S(f)$ to maximize the entropy gain.
In a real example, we have no access to all frequencies but only on those between minus and plus the Nyquist frequency, defined from the sampling interval $\Delta t$ as 

@@

All the quantities of interest are well defined in this range only, so that we are not going to maximize \ref{eq:EntropyGain} over all frequencies, but only on the admissible ones. Our objective becomes:

@@

\par
Now the the objective to maximize is well defined, we can write down the constraints of our problem.
Defining $\bar r_n$ as the sample autocorrelation, we require that the variational solution $S(f)$ for the PSD matches the empirical autocorrelation. This means:

@@

        \includegraphics[width = \linewidth]{Images/Noise and PSD/NormalPSDautocorr.pdf}
